---
title: "PML Course Project"
output: html_document
---

Loading and reading data
```{r}
if(!file.exists("pml-training.csv")){
    download.file("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv", 
                  destfile="pml-training.csv",
                  method="curl")
}
if(!file.exists("pml-testing.csv")){
    download.file("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv",
                  destfile="pml-testing.csv",
                  method="curl")
}
training <- read.csv("pml-training.csv")
testing <- read.csv("pml-testing.csv")

```


```{r}
trainingAdelmo = training[training$user_name=="adelmo",]
unique(trainingAdelmo[trainingAdelmo$classe=="A", c("cvtd_timestamp")])
tAdelmoTimestamp1 <- trainingAdelmo$raw_timestamp_part_1[trainingAdelmo$classe=="A"]
length(tAdelmoTimestamp1)/length(unique(tAdelmoTimestamp1))
plot(x=trainingAdelmo$num_window[1:800],col=trainingAdelmo$new_window[1:800],pch=19)
plot(trainingAdelmo$num_window, col=(trainingAdelmo$classe), pch=20)
```

num_window mean probably the num of second

belt, arm, forearm, dumbell
roll, pitch, yaw: kurtosis, skewness, max, min, amplitude, avg, stddev, var - 27
gyros, accel, magnet: x, y ,z - 9
total_accel, var_total_accel - 2

38*4 = 152
X, user_name, 
raw_timestamp_part_1 - number of seconds from 1970-01-01
raw_timestamp_part_2 - number of microseconds
cvtd_timestamp - date
new_window - yes/no
num_window - second
classe - [A, B, C, D, E]

Trying to understand in which groups min, max, avg etc. were calculated
```{r}
groupsAdelmo <- c(0, cumsum(trainingAdelmo$new_window=="yes")[1:length(trainingAdelmo$new_window)-1])
```

These "summary" values are messed up and there are no values in the test set, so we just remove them.
belt, arm, forearm, dumbell
roll, pitch, yaw - 3
gyros, accel, magnet: x, y ,z - 9
total_accel - 1

```{r}
training <- (subset(training,select = !names(training) %in% (grep("kurtosis|skewness|max|min|avg|amplitude|stddev|var", names(training), value=T))))
dim(training)


library(caret)
library(randomForest)

train52 <- subset(training,select = !names(training) %in% c("X","user_name","raw_timestamp_part_1","raw_timestamp_part_2","cvtd_timestamp","new_window","num_window"))

```


Now we'll use cross validation to select how many features we'll use in random forest algorithm.
```{r cache=TRUE}
res <- rfcv(train52[,-53], train52[,53], cv.fold=5, step = 0.5)
res$error.cv
```
Now let's fit the model with random forest with default parameters and choose 13 most important variables
```{r cache=TRUE}
modelFit <- randomForest(x = train52[,-53], y=train52$classe, importance=TRUE)

```

```{r}
imps <- importance(modelFit)[,c("MeanDecreaseGini")]
impVars <- names(imps)[order(imps, decreasing = T)][1:13]
train13 <-  subset(train52,select = names(train52) %in% c(impVars, "classe"))
```